---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library(tibble)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# unienrollment

<!-- badges: start -->
<!-- badges: end -->

The goal of unienrollment is to provide an engaging dataset for University professors and administrators who are learning R, the [tidyverse](http://tidyverse.org), and [ggplot2](http://ggplot2.tidyverse.org/). The package contains two datasets: `enrollment` and `income`. Both are derived from Statistics Canada data products that rely on the [Postsecondary Student Information System (PSIS)](http://www23.statcan.gc.ca/imdb/p2SV.pl?Function=getSurvey&SDDS=5017).

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("paleolimbot/unienrollment")
```

If you can load the package, you're all set!

```{r}
library(unienrollment)
```

## Canadian postsecondary enrollment

The `enrollment` dataset contains counts of the number of students enrolled in Canada with a given degree type and program class. The dataset is also divided by year and gender. Each row represents a cohort of students who share an enrollment year, a degree type, a program class, and a gender.

```{r enrollment}
enrollment
```

## Employment income of postsecondary graduates

The `income` dataset contains the median empoyment income of postsecondary students who graduated in 2010 and 2011 after 2 years and 5 years. Each row represents a cohort of students who share a graduation year, a degree type, a program class, and a gender.

```{r income}
income
```
